---
title: "Knitr tips"
author: "Michael Friendly"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document records a few tips and tricks I've learned in using `knitr`, `pandoc` and other `R` tools
for writing articles and other documents using R markdown.

### YAML tips

A basic requirement for an R markdown `.Rmd` file is a header in YAML format, essentially a list of
tags and values used when formatting the document.  This is what I got when I first created this document
in R Studio, using `File -> New File -> R markdown`, where my name had already been recorded.

```
---
title: "Knitr tips"
author: "Michael Friendly"
date: "5/13/2020"
output: html_document
---
```

Now, this might be OK, but what if I want the date to be updated automatically for the current version?
This is where the power of knitr and R combine to make this easier.  Just use an "`r expression`"
in the `date:` field.

```
---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
```




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
